---
title: "ICE Detention Levels and COVID-19 Plots"
author: "Nathan Craig"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    number_sections: true
    anchor_sections: true
    keep_md: yes
    code_download: true
---

# Introduction

This document provides plots of data reported on the Immigration and Customs Enforcement [Guidance on COVID-19](https://www.ice.gov/coronavirus) website. On Friday March 13, 2020 ICE suspended family and social visitation. On March 27, 2020 ICE [established](https://web.archive.org/web/20200327175825/https://www.ice.gov/coronavirus) the Guidance on COVID-19 web page and indicated the site would be updated frequently. Shortly afterwards I began logging the data on a daily basis, occasionally relying on the Internet Archive's Wayback Machine's [regular scrapes](https://web.archive.org/web/20200401000000*/https://www.ice.gov/coronavirus) of the page to pick up days that I missed.

Results of those scrapes are contained in a [github](https://github.com/n8craig/ICE-COVID-19) repository, and additional details reported on my [website.](https://ncraig.netlify.app/)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

```{r Load Libraries}
# Load Libraries
library(readr)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(plotly)
library(janitor)
library(knitr)

options(digits=3)
opts_chunk$set(results = 'asis',
               comment = NA,
               prompt = FALSE,
               cache = FALSE)

# Turn off scientific notation
options(digits=5, scipen=15)
```

```{r load-dataset}
# Load Dataset
df_summary <- read_csv("./../data/covid_summaries.csv", 
    col_types = cols(Date = col_date(format = "%m/%d/%Y"), 
        `Total Deaths` = col_double(), `Total COVID-19 Confirmed in Custody` = col_double())) %>% 
  clean_names()
```

```{r ICE-Detention-Population}

# ICE Detention Population Over Time
p <- ggplot(df_summary, aes(x=date, y=total_detained))+
  geom_line()+
  geom_point()+
  geom_smooth()+
  labs(
    title = "ICE Detention Population Over Time",
    x = "Date",
    y = "Total Detained"
  )
  ggplotly(p)

```

```{r}
b_inaug <- df_summary %>% 
  filter(date == "2021-01-20") %>% 
  pluck("total_detained")

lowest <- df_summary %>% 
  filter(date == "2021-03-09") %>% 
  pluck("total_detained")

yesterday <- df_summary %>% 
  filter(date == Sys.Date()-1) %>% 
  pluck("total_detained")

difference <- yesterday-lowest

detention_change <- yesterday - lowest

percent_change <- round((difference/lowest)*100,0)

```


When Biden took office, the detained population was `r b_inaug`. The lowest detention population was `r lowest` reported by ICE between March 9-15, 2021  which was just under three months into the Biden administration. However, by March 16 the detained population began rising again. As of `r format(Sys.Date(), "%B %e, %Y")`, it is `r yesterday` which represents an increase of `r detention_change` individuals from the lowest point and a `r percent_change`% change from that value.


# Active COVID-19 Cases in ICE Detention
```{r Total-Confirmed-COVID-19}
# Total Confirmed COVID-19 Over Time
p <- ggplot(df_summary, aes(x=date, y=total_covid_19_confirmed_in_custody))+
  geom_line()+
  geom_smooth()+
   labs(
    title = "Total Number of Confirmed COVID-19 Cases in ICE Detention",
    x = "Date",
    y = "Total COVID-19 Confirmed in Custody"
  )
ggplotly(p)

```

# Cumulative COVID-19 Cases in ICE Detention

```{r Cumulative-COVID-19}
# Cumulative COVID-19
ggplot(df_summary, aes(x=date, y=total_cumulative_covid_19))+
  geom_line()+
  geom_smooth()+
   labs(
    title = "Cumulative COVID-19 Cases in ICE Detention",
    x = "Date",
    y = "Total Cumulative COVID-19"
  )

```

# Total Number of COVID-19 tests in ICE detention
Note there is no appreciable increase in the rate of tests after January 20, 2021 when Biden was inaugurated. Based on data reported by ICE, the Biden administration does not appear to have accelerated the rate of COVID-19 testing in ICE detention.

```{r Total-COVID-19-Tests}
# Total COVID-19 Tests
ggplot(df_summary, aes(x=date, y=total_tested))+
  geom_line()+
  geom_smooth()+
   labs(
    title = "Total Number of COVID-19 Tests in ICE Detention Population \nOver Time",
    x = "Date",
    y = "Total Tested"
  )

```


```{r}
df_summary %>%
  mutate(normalized = total_tested/total_detained) %>% 
  ggplot(aes(x = date, y = `normalized`))+
  geom_line()+
  geom_smooth()+
  labs(title = "Ratio Total Tested/Total Detained",
       x = "Date",
       y = "Total Tested/Total Detained")
```

# Number of Deaths in ICE Detention

```{r Total-Deaths-in-ICE-Custody}
# Total Deaths in ICE Custody
ggplot(df_summary, aes(x=date, y=total_deaths))+
  geom_line()+
  geom_smooth()+
   labs(
    title = "Total Number of Deaths in ICE Detention Over Time",
    x= "Date",
    y = "Total Deaths"
  )
```

