Earlier versions of this project used date in the format of Month, Day, Year. This came from when I was manually copying the files and putting them into Excel. So that new data would fit with old data, I maintained that date format.

On 2-25-2022, the scraper broke. As I was digging into the files, I am seeing that date is recorded in a non-conventional way. I am going to change the way date is reported so that it is more standard.

This file contains code that could be used to take the existing `covid_summaries.csv` file, convert the date, and save it again in the new format.

The plan is to change over all of the date scraping to record date in the standard format for R.


```{r}
library(lubridate)
```

```{r}
# Read existing CSV file
# This should be a copy with dates formatted wrong.
df <- read.csv(here::here("data/covid_summaries.csv"))
```

```{r}
# Convert date into conventional format
df <- df %>% 
  mutate(Date = mdy(Date))
```

```{r}
# Write out file
write.csv(df, here::here("data/covid_summaries.csv"))
```

